paper

### 2024-01-23 Toronto_Victims_of_Crimes/outputs/paper/paper.qmd
Update paper.qmd file and rendered it.

# Read CSV
unedited_data <- read.csv("Toronto_Victims_of_Crimes/inputs/data/unedited_data.csv")

@@

### should be added using BibTeX, reference R and any R pckgs you use, as well as the dataset.

>>>>

# list files
list.files(path = "Toronto_Victims_of_Crimes/inputs/data/unedited_data.csv")
unedited_data <- list.files(path = "Toronto_Victims_of_Crimes/inputs/data/unedited_data.csv")

@@

### should be added using BibTeX,
